Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-10 ms.tex
fix repeat

In addition to our solutions which neglect thermal conduction and
radiative cooling, we explore a smaller set of simulations including
these effects explicitly, as marked by dagger symbols in Table
\ref{table:models}.  For solutions which are far from being thermally
unstable when cooling is neglected (e.g., $M_{\bullet} =
10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
radiative cooling has little effect on the key properties of the flow,
e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
marginally thermally stable, including radiative losses acts to
decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
greater fractional amount.  We calculated solutions with radiative
cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
expected mass loss rates (see Fig.~\ref{fig:vwSources}).  Solutions
found to be unstable for all values of $\eta$ are marked in boldface
as ``TI" in Table \ref{table:models}, with the unstable values of
$\eta$ provided in the final column.

Thermal conduction, by contrast, results in only order unity changes
to our results for the stagnation radius (and hence the accretion
rate) for our fiducial value of the saturation parameter $\phi =0.1$.
% Conduction may, however, offset the effects of radiative cooling in
% making the flow more thermally stable
% (e.g.~\citealt{Zakamska&Narayan03}).

In addition to our solutions which neglect thermal conduction and
radiative cooling, we explore a smaller set of simulations including
these effects explicitly, as marked by dagger symbols in Table
\ref{table:models}.  For solutions which are far from being thermally
unstable when cooling is neglected (e.g., $M_{\bullet} =
10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
radiative cooling has little effect on the key properties of the flow,
e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
marginally thermally stable, including radiative losses acts to
decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
greater fractional amount.  We calculated solutions with radiative
cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
values of $\eta = 0.02, 0.2,$ and 0.6, spanning the physical range of
expected mass loss rates for the halo average star formation
histories (see figure.  Solutions found to be unstable for all values of $\eta$
are marked in boldface as ``TI" in Table \ref{table:models}, with the
unstable values of $\eta$ provided in the final column.

>>>>

In addition to our solutions which neglect thermal conduction and
radiative cooling, we explore a smaller set of simulations including
these effects explicitly, as marked by dagger symbols in Table
\ref{table:models}.  For solutions which are far from being thermally
unstable when cooling is neglected (e.g., $M_{\bullet} =
10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta =
0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the inclusion of
radiative cooling has little effect on the key properties of the flow,
e.g., stagnation radius, mass accretion rate, $\dot{q}_{\rm
  heat}/|\dot{q}_{\rm rad}|$.  However, for solutions that are only
marginally thermally stable, including radiative losses acts to
decrease the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a
greater fractional amount.  We calculated solutions with radiative
cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and for all
core galaxies with $v_w=600 $ km s$^{-1}$, each for three different
values of $\eta = 0.02, 0.2, 0.6$, spanning the physical range of
expected mass loss for continuous star formation (see
Fig.~\ref{fig:vwSources}).  Solutions found to be unstable for all
values of $\eta$ are marked in boldface as ``TI" in Table
\ref{table:models}, with the unstable values of $\eta$ provided in the
final column.
